\section{Part D}%
\label{closedloopy}

D1 during the coursework, multiple softwares were used to facilitate collaboration efforts. 
these softwares included teams to meet as a group to distribute workload and talk in real 
time if this was needed for collaboration efforts, during work on section a, microsoft 
whiteboard was used to pool together ideas and work in one space, that way everyone 
could be on the same page and work as one. during the coding efforts, github was used to
upload code on a regular basis for debugging. if one group member got stuck while coding
their code would be uploaded to github for the other group members to advance the code.
the github repository can be found here; \href{https://github.com/ELE2024-Controls/Coursework}{[here]}, using github increased productivity
massively, rather than one person getting stuck on a single piece of code and holding 
everyone else up. all group members could pitch in to accelerate the coding process
and prevent holdups. Throughout all parts of the coursework, whatsapp and discord were
used to schedule meetings or request information or help from the group and to upload pdf
files showing progress. the group chat was also used to make announcements, such as 
completing a piece of code or new uploads to the repository.

D2 - work was distributed evenly, with collaboration efforts being made where necessary
     the group contributed where they needed to, which led to the work being completed
     on time with no disagreements within the group
   
   - all group members attended scheduled meetings and spent as much time as was necessary 
     to complete work or recieve tasks, this sometimes led to meetings being 3 hours long
     in the case of a whiteboard collaboration session. but as this was necessary to 
     complete the task, the team stayed
   
   - productivity within the group was excellent, for example. during the progression of 
     section B, one group member would get stuck on debugging a piece of code they wrote.
     request help in the whatsapp and the code would be uploaded to github. picked up by 
     another group member and debugged and completed in a timely manner.

   - group members recognised that this task was important to all of us, so there was no
     issue or embarassment requesting help from the group as everyone within the group 
     knew that this task was a team effort, and the extra work one member put in to aid 
     another member would also benefit their mark too at the end of the task. 

D3 the only real problem faced was in task delagation, with one group member completing 
section a themselves, it was later found out during the coding of section b, that the 
wrong equation was used in defining the system (eg a non-linear spring was used in place
of an elastic one). this set the group back a few days while effort had to be redirected
to correct the error, linearise again and redo transfer functions and rewrite certain
areas of affected code, but the group members were able to pick up on this and correct 
it in a timely manner.